---
title: "Data Science Intro Fish"
format: html
editor: visual
---

## Answering Questions

-   I think being a data scientist is about using data to make observations, gain insights, and learn about potential relationships and patterns. There is so much to data science as a discipline that all works together to create the overarching picture of the subject: coding, modeling, analysis, data cleaning, model writing, etc.. With that in mine, being a data scientist to me starts with the desire to want to learn something more from data than what originally meets the eye.

-   Between data scientists and statisticians, there are many similarities. To start, many statistics courses nowadays use R, SAS, and other languages in order to analyze data and make conclusions; I presume data scientists do the same. However, statistics seems more preoccupied with forming a nicely worded conclusion from a previously stated hypothesis, whereas data science is moreso aiming to analyze large data sets for any underlying information. Also, data scientists seem to have a wide range of skills for automation of tasks and analysis/cleaning of large data sets, while statistics seems to follow a structured series of tasks in order to complete a specific analysis.

-   I definitely see myself as more of a statistician than a data scientist. I honestly still struggle with how to decipher the two, but I know that I have much more confidence in my ability to solve a statistics problem as opposed to a data science problem. In reality, though, data scientist positions are becoming more and more useful/desirable as they have a wide range of capabilities, so I hope to change this answer sooner rather than later!

## R Code Chunks

Here, I pasted the code from the assignment.

```{r chunk 1}
y <- density(iris$Petal.Width)
class(y)
typeof(y)
str(y)
```

In the code chunk above, I created an object y that takes on the values of pedal widths from a very popular R data set, iris. Then, I checked the class, type, and structure of this newly defined object.

I am now going to plot this object, y.

```{r chunk 2}
#| echo: false
plot(y, main = "Plot of Object y")
```
